Effects of the body force on the evacuation dynamics

### 2019-12-30 paper.tex
comente un par de cosas en el apendice porque no compilaba
Update paper.tex
agregue texto que explica el diagrama fundamental

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_nocomp}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_comp}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}

>>>>

In this section, we present the results corresponding to the corridor geometry. We show how the overall dynamic of the system changes depending on the $k$ value associated to the body force in the original SFM.\\

In Fig ... we show the flow as a function of the global density (fundamental diagram). \ref{flow_density_no_body_force} corresponds to non body force ($i.e k_n=0$), \label{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5. Each curve correspond to a different friction value. The circles correspond to the value of the original SFM ($\\kappa = 2.4~E5$), the "+" symbol correspond to the original value increased by a factor of five and triangles correspond to the original value increased by a factor of ten. \\

According to most of the empirical measurements, the flow decreases for high enough values of density because the motion becomes jammed. Notice that the original friction does not produce a reduction of the flow when there is no body force but when the body force is included (with the original value), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher values of density. When the density is five times the original value, the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force). The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$. When the friction is increased by a factor of ten, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with body force and without body force). \\

This result suggests that even including the body force, the original SFM requires an increment of the friction in order to reproduce the flow reduction reported in empirical measurements.

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}
